Adaptative neigbouring methods applied to telephonic base stations

### 2024-08-21 article.tex
Correction d'un bout de mise en page

It consists of a substantial collection of $108\,838$ entries, encompassing 29 distinct features of a size of $\unit[16.7]{Mo}$.
Each row of the database corresponds to detailed information regarding a specific BS. For the scope of this study,
our analysis will focus on the fields outlined in Table~\ref{table:data_columns}.
\begin{table}
    \centering
    \caption{Description of the main database columns used in the experiments}
    \label{table:data_columns}
    \begin{tabular}{ll}
        \toprule
        \textbf{Column} & \textbf{Description} \\
        \cmidrule(lr){1-2}
        \textsl{id\_station\_anfr} & \acrshort{anfr} \acrshort{bs} ID \\ 
        \textsl{nom\_op} & Name of the provider \\
        \textsl{$x$, $y$, latitude, longitude} & Base station coordinates \\ 
        \textsl{nom\_reg, nom\_dep, nom\_com} & Additional location information \\  
        \textsl{site\_2g, 3g, 4g, 5g} & Technology used by the \acrshort{bs} \\ 
        \bottomrule
    \end{tabular}
\end{table}

@@

\subsection{Filtering the database}
As seen before this database is really huge, as a matter of fact we will only work on a portion of it.

@@

>>>>

It consists of a substantial collection of $108\,838$ entries, encompassing $29$ distinct features of a size of $\unit[16.7]{Mo}$.
Each row of the database corresponds to detailed information regarding a specific BS. For the scope of this study,
our analysis will focus on the fields outlined in Table~\ref{table:data_columns}.
\begin{table}
    \centering
    \caption{Description of the main database columns used in the experiments}
    \label{table:data_columns}
    \begin{tabular}{ll}
        \toprule
        \textbf{Column} & \textbf{Description} \\
        \cmidrule(lr){1-2}
        \textsl{id\_station\_anfr} & \acrshort{anfr} \acrshort{bs} ID \\ 
        \textsl{nom\_op} & Name of the provider \\
        \textsl{$x$, $y$, latitude, longitude} & Base station coordinates \\ 
        \textsl{nom\_reg, nom\_dep, nom\_com} & Additional location information \\  
        \textsl{site\_2g, 3g, 4g, 5g} & Technology used by the \acrshort{bs} \\ 
        \bottomrule
    \end{tabular}
\end{table}

@@

\subsection{Filtering the main database}
As seen before this database is really huge, as a matter of fact we will only work on a portion of it.

@@

\subsection{Additional database}
In order to compare the results of city detection, we needed a reference database. We therefore used the population data provided by INSEE.
[Pas sur de l'utilité de présenter cette base en fait, ptet juste la principale suffit]
